---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(tidyverse)
library(definer)
```

# definer

<!-- badges: start -->
<!-- badges: end -->

The goal of definer is to make it easy to apply field maps / survey data definitions to datasets with integer coding.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("davisadamw/definer")
```
## Example

A very basic example of what this does:
```{r}
# create a definitions dataset linking coded values of various variables to what they represent
def_list <- tibble(variable   = c("A", "A", "B", "B", "C"),
                   value      = c(1,   2,   1,   2,   1),
                   definition = c("cat", "dog", "fred", "george", "lonely")) %>%
  def_prep(variable, value, definition, drop_solos = FALSE)

# make a little source dataset to run this on
source_data <- tibble(ID = c("A1", "A2", "A3"),
                      A  = c(1, 1, 2),
                      B  = c(2, 1, 2),
                      C  = c(1, 1, 1))

# run the mass recoding
updated_values <- def_recode_all(source_data, def_list)

# display the results side-by-side
left_join(source_data, updated_values, 
          by = "ID", suffix = c("_old", "_new"))
```

## ToDos
There are three updates / improvements I have in mind before I'm ready to call this the 0.0.1 version:

* Dictionary (output of `def_prep()` and input of all the other functions) as an S3 class with print and other methods.
* Let `def_recode_all()` take multiple values to the `.default` and `.missing` arguments. If these are named, they should get passed into the recoding for the matching variables.
* More flexible inputs for `def_prep()` ... let it handle 3-column data frames without user needing to specify which column is which. 

One longer-term one that would require a bit more input:

* Versions of `def_prep()` or other preparatory functions that can take in various ~raw dictionary formats. Basically wrap everything I do in the import-and-clean-definitions vignette but for a few standard dictionary types. Dunno how many there are out there or whether this should be up to the user, but since this is the hardest part of the process, it makes sense to me to automate at least a few common cases.
